Implementation of Parallel Algorithms for ARIMA in Distributed Database Systems

### 2013-10-05 draft.tex
Continue

@@

{\bf keywords}: distributiv, parallel computation, database, machine
learning, big data, ARIMA

@@

\begin{figure}[ht]
  \begin{centering}
    \includegraphics[angle=-90,scale=0.4]{gp_time_vs_size}
  \end{centering}
  \caption{\label{fig:gp_time_size} We fit a time series with length
    of $10^8$ using different chunk sizes. The execution times are
    around $400$ $\sim$ $500$ secs, and are quite stable. }
\end{figure}

\begin{figure}[ht]
  \begin{centering}
    \includegraphics[angle=-90,scale=0.4]{pg_time_vs_size}
  \end{centering}
  \caption{\label{fig:pg_time_size} We fit a time series with length of
    $10^8$ using different chunk sizes. The execution times are around
    $400$ $\sim$ $500$ secs, and are quite stable. }
\end{figure}

\begin{table}[ht]
  \begin{tabular}{|l|l|l|l|}
    \hline
    ~ & MADlib on GPDB & MADlib on Postgres & R's arima function \\ \hline
    Execution Time (sec) & 364.4 & 1391.9 & 1964.4 \\ \hline
  \end{tabular}
  \caption{\label{tbl:compare_R} Here we compare the execution times of ARIMA model fitting in R and in MADlib on Greenplum Database and PostgreSQL database. }
\end{table}

>>>>

\institute{Predictive Analytics Team, Pivotal Inc.}

@@

{\bf keywords}: distributive, parallel computation, database, machine
learning, big data, ARIMA

@@

\begin{figure}[ht]
  \begin{centering}
    \includegraphics[angle=-90,scale=0.4]{gp_time_vs_size}
  \end{centering}
  \caption{\label{fig:gp_time_size} We fit time series with different
    lengths with the chunk size $10^5$ using MADlib's ARIMA function
    on Greenplum database. The red line is the fit to $t = \alpha l$, where $t$
    is the execution time and $l$ is the length of the time series.}
\end{figure}

\begin{figure}[ht]
  \begin{centering}
    \includegraphics[angle=-90,scale=0.4]{pg_time_vs_size}
  \end{centering}
  \caption{\label{fig:pg_time_size} We fit time series with different
    lengths with the chunk size $10^5$ using MADlib's ARIMA function
    on PostgreSQL database. The red line is the fit to $t = \alpha l$, where
    $t$ is the execution time and $l$ is the length of the time
    series.}
\end{figure}

\begin{table}[ht]
  \begin{tabular}{|l|l|l|l|}
    \hline
    ~ & MADlib on GPDB & MADlib on Postgres & R's arima function \\ \hline
    Execution Time (sec) & 364.4 & 1391.9 & 1964.4 \\ \hline
  \end{tabular}
  \caption{\label{tbl:compare_R} Here we compare the execution times
    of ARIMA model fitting in R and in MADlib on Greenplum Database 
    and PostgreSQL database. The time series used to fit the ARIMA 
    model has a length of $10^8$. Note that running MADlib's ARIMA
    on Postgres is not only faster but also uses much less memory (0.1\%). 
    Running this data set in R (50G memory) uses almost 70\% of the
    machine's memory.}
\end{table}

\begin{figure}[ht]
  \begin{centering}
    \includegraphics[angle=-90,scale=0.4]{gp_time_vs_seg}
  \end{centering}
  \caption{\label{fig:gp_time_seg} We fit a time series with length of
    $10^8$ using different numbers of segments in Greenplum
    database system.}
\end{figure}
